A Large-Scale Study of the Use of Eval in R

### 2020-08-21 inst/paper/main.tex
more stuff

- Why eval is used in R
- What the community says about using eval
- What existing tools do about eval
- Do people use eval for obvious things like looking up variable, if yes, it is
because they are unaware of alternatives?
- Why automating the transformation is a hard problem.
- What is the goal of the work? To replace eval with code for static analyssi or
for consumption by the users of the language?
- We only permit transformations that preserve code behavior?
- Do we accept overly complex code as the output?

What are the challenges? Why is it not trivial?
- Do we handle aliasing of eval?
- Simple cases can be subtle? (laziness for ex.

Why can't we replace eval(code) by code?

Intended user of the technique? Which version of R is targeted.

Contributions:
- Describe the use of eval in R
- Develop a tool to replace evals guided by dynamic traces

- cannot replace with (cite study of with construct).

@@

@@

@@

There are four different kinds of \texttt{eval} in the \emph{base} package:  \texttt{eval}, \texttt{evalq}, \texttt{eval.parent},  \texttt{local}.
The most important one is \texttt{eval}:

@@

\subsubsection{A taxonomy of \texttt{eval}}

We first classify \texttt{eval} depending on the resolved expression, \emph{i.e.} the first argument of \texttt{eval} after all possible function calls and symbol resolution in it have been executed.

@@

\subsection{\texttt{base}}

\section{Related Work}
eval has been widely discussed in the research literature for the challenges it
imposes for code comprehension and automated code analyses.
Perhaps, EvalMenDo is the most popular exposition of eval and its
challenges for JavaScript.

\textbf{Aviral}
- javascript
- ruby
- php

\section{Conclusion}
\textbf{*}

\section*{Acknowledgment}

\section*{References}

>>>>

@@

\cite{ecoop11}

@@

There is some work on

@@

There are four different kinds of \c{eval} in the \emph{base} package:  \c{eval}, \c{evalq}, \c{eval.parent},  \c{local}.
The most important one is \c{eval}:

@@

\subsubsection{A taxonomy of \c{eval}}

We first classify \c{eval} depending on the resolved expression, \emph{i.e.}
the first argument of \c{eval} after all possible function calls and symbol
resolution in it have been executed.

@@

\subsection{base}

\section{Conclusion}

\bibliographystyle{IEEEtran}
\bibliography{bib/bibliography,bib/jv}
